### 2018-08-05 pipeline.tex
Carlottas last corrections

The MQ+LFQ pipeline results were obtained starting at the Supplemental table 1 from the MaxLFQ paper supplemental data \footnote{\href{http://www.mcponline.org/content/13/9/2513/suppl/DC1}{Link to the supplemental data http://www.mcponline.org/content/13/9/2513/suppl/DC1}} \cite{Cox2014}, which are available as an excel file. The results of the MQ+Rob pipeline employed the Levenberg-Marquardt-minimised peptide intensities stored in the peptides.txt file contained in the spectraHeLaEColi.zip in the supplemental data.

@@

Relative quantification i.e the computation of $\log_2$(ratios), or logarithm base 2 fold changes, $\log_2(FC)$ (\ac{log2FC}) was performed using the MSqRob package \cite{Goeminne2016} by passing the peptide summary file from moFF (Compomics+Rob) or the peptides.txt from MaxQuant (MQ+Rob). Prior to quantification, the data was preprocessed using the \texttt{preprocess\_MSnSet()} function. In a nutshell, (I) MS1 apex intensities were $log_2$ transformed, (II) quantile normalized, (III) peptides belonging to protein groups that contained one or more proteins that were also present in a smaller protein group were discarded \cite{Goeminne2016}, and (IV) protein groups with only 1 peptide were dropped.

@@

Quantification in the MQ+LFQ pipeline was executed using the LFQ intensity columns stored in the supplemental data file. Intensities were $\log_2$ transformed and averaged. The difference between conditions H and L was taken as estimate of the log2FC. Significance was evaluated by means of the two-tailed Welch Two Sample t-test implemented in the \texttt{t.test()} function in R. P-values were corrected using the FDR method implemented in the \texttt{p.adjust()} function in R with the "fdr" method.

@@

The 1\% FDR cutoff selected PSMs with a score higher than 78, which translated to a confidence of at least 65\% (see figure \ref{figure:qc_validation} B).

@@

The SearchGUI and PeptideShaker developers recommend using Uniprot-formatted databases for optimal performance of their tools \footnote{\href{https://github.com/compomics/searchgui/wiki/DatabaseHelp}{Database formatting guide https://github.com/compomics/searchgui/wiki/DatabaseHelp}}. This is due to the software making use of protein annotations to improve the protein inference step. In any case, a consistent formatting in the FASTA databases is required to use the tools. Thus, the development of sequence databases featuring consistent FASTA identifiers is highly advisable to make the best use of the data and improve the interplay with nost just these but many other tools too.

>>>>

The MQ+LFQ pipeline results were obtained starting at the supplemental table 1 from the MaxLFQ publication \footnote{\href{http://www.mcponline.org/content/13/9/2513/suppl/DC1}{Link to the data http://www.mcponline.org/content/13/9/2513/suppl/DC1}} \cite{Cox2014}, which are available as an excel file. The results of the MQ+Rob pipeline employed the Levenberg-Marquardt-minimised peptide intensities stored in the peptides.txt file contained in the spectraHeLaEColi.zip in the supplemental data.

@@

Relative quantification i.e. the computation of $\log_2$(ratios), or logarithm base 2 fold changes, $\log_2(FC)$ (\ac{log2FC}) was performed using the MSqRob package \cite{Goeminne2016} by passing the peptide summary file from moFF (Compomics+Rob) or the peptides.txt from MaxQuant (MQ+Rob). Prior to quantification, the data was preprocessed using the \texttt{preprocess\_MSnSet()} function. In a nutshell, (I) MS1 apex intensities were $log_2$ transformed, (II) quantile normalized, (III) peptides belonging to protein groups that contained one or more proteins that were also present in a smaller protein group were discarded \cite{Goeminne2016}, and (IV) protein groups with only 1 peptide were dropped.

@@

Quantification in the MQ+LFQ pipeline was executed using the LFQ intensity columns stored in the data file. Intensities were $\log_2$ transformed and averaged. The difference between conditions H and L was taken as estimate of the log2FC. Significance was evaluated by means of the two-tailed Welch Two Sample t-test implemented in the \texttt{t.test()} function in R. P-values were corrected using the FDR method implemented in the \texttt{p.adjust()} function in R with the "fdr" method.

@@

The 1\% FDR cutoff selected PSMs with a score higher than 78, which translated to a confidence (probability of the match being true) of at least 65\% (see figure \ref{figure:qc_validation} B).

@@

The SearchGUI and PeptideShaker developers recommend using Uniprot-formatted databases for optimal performance of their tools \footnote{\href{https://github.com/compomics/searchgui/wiki/DatabaseHelp}{Database formatting guide https://github.com/compomics/searchgui/wiki/DatabaseHelp}}. This is due to the software making use of protein annotations to improve the protein inference step. In any case, a consistent formatting in the FASTA databases is required to use the tools. Thus, the development of sequence databases featuring consistent FASTA identifiers is highly advisable to make the best use of the data and improve the interplay with not just these but many other tools too.
